---
project:
  title: "day-09"
  output-dir: docs

format:
  html:
    self-contained: true
    
execute:
  echo: true
---

```{r}
library(dplyr)
library(tidyverse)
library(visdat)
library(broom)
```

```{r}
vis_dat(airquality)
```

```{r}
airquality_cleaned <- airquality %>% 
  distinct()
vis_dat(airquality_cleaned)
```

```{r}
# Remove
airquality_cleaned <- airquality %>% 
  drop_na()

vis_dat(airquality_cleaned)
```

# To create the linear regression model, I used Ozone and Temperature to measure their relationship. I think this is a valid model because it is statistically significant and because Ozone and temperature usually have a strong relationship.

```{r}
lm_model <- lm(Ozone ~ Temp, data = airquality_cleaned)
summary(lm_model)
```

# The R-squared represents that the ozone (dependent variable) is 48.8% predicatable by temperature (independent variable). When looking at the plot below, it is important to recognize that there are a few outliers that could make a difference, but overall this data looks the best.

```{r}
plot(lm_model)
```

```{r}
predicted_data <- augment(lm_model, data = airquality_cleaned)
head(predicted_data)
```
```{r}
correlation <-round(cor(predicted_data$Ozone, predicted_data$.fitted), 2)
```

```{r}
ggplot(predicted_data, aes(x = .fitted, y = Ozone)) +
  geom_point(color = "blue", alpha = 0.6) + 
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") + 
  labs(
    title = "Actual vs. Predicted Ozone Levels",
    x = "Predicted Ozone (ppb)",
    y = "Actual Ozone (ppb)",
    subtitle = paste("Correlation:", correlation)
  ) +
  theme_minimal()
```

